Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-06-21 paper/paper.tex
Fix amplitude calculation in the paper, again

Since wave action is variance divided by the intrinsic frequency $\sigma$,
and variance scales with $ga^2$, the modulation of the amplitude is proportional
to the square root of the modulation of wave action.

\begin{equation}
\label{eq:wave_amplitude_modulation}
\widetilde{a}(\psi) = a \sqrt{
  \dfrac{g}{\widetilde{g}}
  \dfrac{\sigma}{\widetilde{\sigma}}
  \dfrac{\widetilde{N}}{N}}
=
  \left( \dfrac{\widetilde{g}}{g} \right)^{0.75}
  \left( \dfrac{\widetilde{k}}{k} \right)^{0.25}
  \left( \dfrac{\widetilde{N}}{N} \right)^{0.5}
\end{equation}
To the 1$^{st}$ order in $\varepsilon_L$, the amplitude modulation is then:

\begin{equation}
\label{eq:wave_amplitude_modulation_order1}
\dfrac{\widetilde{a}}{a} = 
  \left( \dfrac{\widetilde{g}}{g} \right)^{0.75}
  \left( 1 + \varepsilon_L \right)^{0.75}
\end{equation}

To determine $\widetilde{\sigma}$, we will need to evaluate the modulation of
the gravitational acceleration at the surface of the long wave.

>>>>

Since wave action is energy divided by the intrinsic frequency $\sigma$,
and energy scales with $ga^2$, the modulation of the amplitude is readily
related to the modulations of gravity, wavenumber, and action:

\begin{equation}
\label{eq:wave_amplitude_modulation}
\dfrac{\widetilde{a}}{a} = \sqrt{
  \dfrac{g}{\widetilde{g}}
  \dfrac{\widetilde{\sigma}}{\sigma}
  \dfrac{\widetilde{N}}{N}}
=
  \left( \dfrac{g}{\widetilde{g}} \right)^{0.25}
  \left( \dfrac{\widetilde{k}}{k} \right)^{0.25}
  \left( \dfrac{\widetilde{N}}{N} \right)^{0.5}
\end{equation}
To the 1$^{st}$ order in $\varepsilon_L$, and using Eqs. \ref{eq:k_short_exact}
and \ref{eq:wave_action_modulation}, we get:

\begin{equation}
\label{eq:wave_amplitude_modulation_order1}
\dfrac{\widetilde{a}}{a} = 
  \left( \dfrac{g}{\widetilde{g}} \right)^{0.25}
  \left( 1 + \varepsilon_L \right)^{0.75}
\end{equation}

To determine $\widetilde{\g}$, we will need to evaluate the modulation of
the gravitational acceleration at the surface of the long wave.
